Motor Vehicle Collisions Reduced Across Toronto During and After the Beginning of the COVID-19 Pandemic

### 2024-01-23 outputs/paper/paper.qmd
Added R citation to paper

The datasets were cleaned and analyzed using `tidyverse` [@citetidyverse], `knitr` [@citeknitr], `janitor`[@citejanitor], `dplyr` [@citedplyr], `ggplot2` [@citeggplot2], and `sf` [@citesf]. Some of the datasets used for the data analysis combined the `Ward Profiles (25-Ward Model)` and `Police Annual Statistical Report - Traffic Collisions` in order to create datasets with the following variables: `collision_type`, `num_of_collisions`, `num_of_pedestrians`, `yearly_collision_num`, and `total_collisions_2017_2023`. `collision`. These variables were formed by mostly created group existing columns and counting the number of rows with certain column variables. The Toronto Police Services has defined MVC under 4 different categories: Fatal, Personal Injury, Fail to Remain, and Property Damage [@citecollisionsdata]. Fatal means that a person was killed during the vehicle collision, personal injury indicates a person was injured during the collision, fail to remain means that the person left the scene before after information was provided regarding the collision, and property damage
indicates that property has been damaged during the collision. With this, the 4 types are possible values under the variable `collision_type`. `num_of_collisions` represents the number of collisions that occurred in either a neighbhourhood in a specific year or the number of collisions of a certain type of a certain year depending on the context. 
`num_of_pedestrians` represents the number of pedestrians that were hit in the vehicle collision.`yearly_collision_num` and `total_collisions_2017_2023` are the count of collisions in a specific year and the total number of collisions from 2017 to 2023 for each Toronto neighbhourhood mentioned in the `Police Annual Statistical Report - Traffic Collisions` dataset. For the dataset regarding Toronto ward profiles, the following variables were created: `ward_name` (indicates the name of the Toronto ward), `pop_num` (represents the population size of Toronto wards as of 2020), and `avg_income` (signifies the average household income of each ward as of 2020).

>>>>

The datasets were cleaned and analyzed using the statistical programming language `R` [@citeR], `tidyverse` [@citetidyverse], `knitr` [@citeknitr], `janitor`[@citejanitor], `dplyr` [@citedplyr], `ggplot2` [@citeggplot2], and `sf` [@citesf]. Some of the datasets used for the data analysis combined the `Ward Profiles (25-Ward Model)` and `Police Annual Statistical Report - Traffic Collisions` in order to create datasets with the following variables: `collision_type`, `num_of_collisions`, `num_of_pedestrians`, `yearly_collision_num`, and `total_collisions_2017_2023`. `collision`. These variables were formed by mostly created group existing columns and counting the number of rows with certain column variables. The Toronto Police Services has defined MVC under 4 different categories: Fatal, Personal Injury, Fail to Remain, and Property Damage [@citecollisionsdata]. Fatal means that a person was killed during the vehicle collision, personal injury indicates a person was injured during the collision, fail to remain means that the person left the scene before after information was provided regarding the collision, and property damage
indicates that property has been damaged during the collision. With this, the 4 types are possible values under the variable `collision_type`. `num_of_collisions` represents the number of collisions that occurred in either a neighbhourhood in a specific year or the number of collisions of a certain type of a certain year depending on the context. 
`num_of_pedestrians` represents the number of pedestrians that were hit in the vehicle collision.`yearly_collision_num` and `total_collisions_2017_2023` are the count of collisions in a specific year and the total number of collisions from 2017 to 2023 for each Toronto neighbhourhood mentioned in the `Police Annual Statistical Report - Traffic Collisions` dataset. For the dataset regarding Toronto ward profiles, the following variables were created: `ward_name` (indicates the name of the Toronto ward), `pop_num` (represents the population size of Toronto wards as of 2020), and `avg_income` (signifies the average household income of each ward as of 2020).
